Modeling the Linux page cache for accurate simulation of data-intensive applications

### 2021-05-20 paper_io_sim.tex
adjusted layout in Fig 4

    \begin{figure*}
        \centering
        \begin{subfigure}{\linewidth}
            \centering
               \includegraphics[width=\linewidth]{result/single/figures/single_errors_v2.pdf}
               \vspace*{-0.7cm}
               \caption{Relative simulation errors (absolute values)}
               \vspace*{0.5cm}
               \label{fig:single_error}
            \end{subfigure}
        \begin{subfigure}{\linewidth}
            \centering
            %    Gray shades represent task phases (read, compute and write).
            %    Lines represent memory usage along pipeline execution time.}
               \includegraphics[width=\linewidth]{result/single/figures/single_memprof_v2.pdf}
               \vspace*{-0.7cm}
               \caption{Memory profiles}
               \vspace*{0.5cm}
               \label{fig:single_memprof}
        \end{subfigure}
        \begin{subfigure}{\linewidth}
            \centering
               \includegraphics[width=1.05\linewidth]{result/single/figures/cached_files_v2.pdf}
               \caption{Page cache content after each I/O operation}
            %    \textcolor{red}{Update real results of 20GB}}
               \label{fig:single_cache}
        \end{subfigure}
        \caption{Single-threaded results (\textit{Exp 1})}
        \end{figure*}

>>>>

    \begin{figure*}
        \centering
        \begin{subfigure}{\linewidth}
            \centering
               \includegraphics[width=\linewidth]{result/single/figures/single_errors_v2.pdf}
               \vspace*{-0.7cm}
               \caption{Relative simulation errors (absolute values)\\ Left: 20-GB files. Right: 100-GB files.}
                \vspace*{0.2cm}
               \label{fig:single_error}
            \end{subfigure}
        \begin{subfigure}{\linewidth}
            \centering
            %    Gray shades represent task phases (read, compute and write).
            %    Lines represent memory usage along pipeline execution time.}
               \includegraphics[width=\linewidth]{result/single/figures/single_memprof_v2.pdf}
               \vspace*{-0.7cm}
               \caption{Memory profiles\\ From top to bottom: real execution, Python prototype, WRENCH cache. Left: 20-GB files. Right: 100-GB files.}
               \vspace*{0.2cm}
               \label{fig:single_memprof}
        \end{subfigure}
        \begin{subfigure}{\linewidth}
            \centering
               \includegraphics[width=\linewidth]{result/single/figures/cached_files_v2.pdf}
               \caption{Page cache content after each I/O operation\\Left: 20-GB files. Right: 100-GB files.}
            %    \textcolor{red}{Update real results of 20GB}}
               \label{fig:single_cache}
        \end{subfigure}
        \caption{Single-threaded results (\textit{Exp 1})}
        \end{figure*}
